%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\vspace{\acvSectionTopSkip}
\cvsectionIcon{Experience}{\faBriefcase}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Summer Intern} % Job title
    {International Centre for Radio Astronomy Research} % Organization
    {UWA, Perth} % Location
    {Nov. 2020 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigated applying the JPEG2000 based webjpip.js library to remotely viewing very large image radio astronomy spectral data cubes.}
        \item {Presented recommendations to AusSRC for development of webjpip.js as a viable product for future SKA use.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Lead} % Job title
    {Autonomous Vehicle Competition - ENGG1000} % Organization
    {UNSW, Sydney} % Location
    {Feb. 2019 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead a team of 6 first-year students to win the courses’ internal track competition.}
        \item {Programmed the autonomous robot in Arduino (C/C++).}
        \item {Applied small motors, laser-cut gears, and servos.}
        \item {Designed and built an effective power distribution system with a 3s LiPO battery and Veroboard.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Member} % Job title
    {Warman Design \& Build Competition, UNSW Qualifier} % Organization
    {UNSW, Sydney} % Location
    {May. 2019 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in a team of 6 to qualify to represent UNSW at the global competition in parallel with studies.}
        \item {Designed and built powerful servo and motor subsystems, and an effective power distribution system with two 3s LiPO batteries.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Awarded Most Advanced Beginner Pilot} % Job title
    {Gliding Club of WA} % Organization
    {Cunderdin, WA} % Location
    {2018 - 2019} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {Student Attendee} % Job title
    {International Astronautical Congress} % Organization
    {Adelaide} % Location
    {Sep. 2017} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {Student} % Job title
    {United Space School} % Organization
    {Houston, TX, USA} % Location
    {Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned and presented a theoretical mission to Mars in a team of 40 international students.}
        \item {Awarded a flown Texas flag for extraordinary achievement, only five were awarded.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
